---
title: "Homework 6"
author: "Ayako Sekiya"
data: "2022-12-01"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```

## Problem 1


To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 

## Problem 2

```{r import}
homicide = 
  read_csv(file = "./data/homicide-data.csv") %>% 
  janitor::clean_names() 
```

#### Data Cleaning

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. The number of unsolved homicides is those for which the disposition is “Closed without arrest” or “Open/No arrest”.Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.

```{r}
homicide_data=
  homicide %>% 
  unite("city_state", city:state, remove = FALSE, sep=", ") %>% 
  group_by(city_state) %>% 
  filter(city_state!="Dallas, TX" & city_state!="Phoenix, AZ" & city_state!="Kansas City, MO"& city_state!="Tulsa, AL") %>%
  filter(victim_race=="White" | victim_race=="Black") %>% 
  mutate(
    resolved = as.numeric(disposition == "Closed by arrest"),
    victim_age = as.numeric(victim_age),
    victim_race = fct_relevel(victim_race, "White")) %>% 
  drop_na(victim_age) %>% 
  select(resolved, victim_age, victim_race, victim_sex)
```

There are `r ncol(homicide_data)` columns and `r nrow(homicide_data)` observations in this data set. The variables are `r names(homicide_data)`. 

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object; apply the broom::tidy to this object

```{r glm}
fit_logistic= homicide_data %>% 
  filter(city_state=="Baltimore, MD") %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) %>% 
  broom::tidy() 
 
```

Obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r stats}
baltimore_df= fit_logistic %>% 
  mutate(log_OR = estimate,
         OR = exp(estimate),
        ci_low=exp(estimate-1.96*std.error),
        ci_high=exp(estimate+1.96*std.error)) %>%
  select(term,log_OR, OR,ci_low,ci_high) %>% 
  filter(term == "victim_sexMale")

baltimore_df %>% 
  knitr::kable(digits = 3)
```

The adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed is 0.426 (95%CI: 0.325, 0.558). In the city of Baltimore the odds of solving homicides among male victims is 0.426 times the odds of solving homicides among female victims. 

#### Mapping 

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r all_cities}
homicide_all=
  homicide_data %>% 
  nest(data=-city_state) %>% 
  mutate(
    models = map(.x=data, ~glm(formula=resolved~victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  mutate(log_OR = estimate,
         OR = exp(estimate),
        ci_low=exp(estimate-1.96*std.error),
        ci_high=exp(estimate+1.96*std.error)) %>%
  select(city_state,term,log_OR, OR,ci_low,ci_high) %>% 
  filter(term == "victim_sexMale")

homicide_all %>% 
  knitr::kable(digits = 3)
```

#### Plotting

Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r plot}
homicide_plot= homicide_all %>% 
  filter(str_detect(term, "victim_sex")) %>% 
  ggplot(aes(x = reorder(city_state, OR), y = OR)) + 
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high)) +
  geom_point(alpha = 0.5 ) +  
  labs(
    title = "Adjusted OR for Solving Homicides comparing Males to Females",
    x = "city, state",
    y = "Adjusted OR") +
  theme(plot.title = element_text(size = 12, face = "bold"),
        legend.position = "none", 
        axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 0.7))
  
homicide_plot

ggsave("results/homicide_plot.pdf", homicide_plot, width = 20, height = 10)

```

Based on this plot, New York, NY has the smallest point estimate for OR. This means that New York has the smallest odds for solving homicides for males compared to females. Albuquerque, NM has the highest point estimate for OR which means that this city has the highest odds for solving homicides for males compared to females. However, Albuquerque has a very wide confidence interval, especially when comparing to other cities.   

## Problem 3

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r import and clean}
birthweight = 
  read_csv(file = "./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate( babysex = as.factor(babysex),
          frace = as.factor(frace),
          malform = as.factor(malform),
          mrace = as.factor(mrace))

sapply(birthweight, function(x) sum(is.na(x)))
```

There is no missing data. There are `r ncol(birthweight)` columns and `r nrow(birthweight)` observations in this data set. The variables are `r names(birthweight)`. 

#### Model Building

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. 

Bqsed on the homework question and the codebook, I will look at the following predictors for my model:
* `gaweeks`: gestational age (weeks)  
* `mrace`: maternal race   
* `ppwt`: mother's pre-pregnancy weight 
* `fincome`: family monthly income (in hundreds, rounded) 

The outcome variable will be:
* `bwt`: baby’s birth weight (grams)

```{r}
model = lm(bwt ~ gaweeks+mrace+ppwt+fincome, data = birthweight) 
```

Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r residual_plot}
birthweight %>% 
  modelr::add_residuals(model) %>%
  modelr::add_predictions(model) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point() +
  labs(
    x = "Fitted values",
    y = "Residuals",
    title = "Model residuals vs fitted values"
  )
```

#### Cross Validation

Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)

```{r main_effect}
maineffect=lm(bwt ~ blength + gaweeks, data =birthweight) %>% 
broom::tidy()
```

One using head circumference, length, sex, and all interactions (including the three-way interaction) between 

```{r interactions}
interactions=
lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = birthweight) %>% 
 broom::tidy()
```

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r cross_validation}
bw_df = crossv_mc(birthweight, 100)

bw_df= bw_df%>% 
    mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

bw_df= bw_df %>% 
  mutate(
    model  = map(train, ~lm(bwt ~ gaweeks+mrace+ppwt+fincome, data = .x)),
    maineffect  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    interactions  = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))) %>% 
  mutate(
    rmse_model = map2_dbl(model, test, ~rmse(model = .x, data = .y)),
    rmse_maineffect = map2_dbl(maineffect, test, ~rmse(model = .x, data = .y)),
    rmse_interactions = map2_dbl(interactions, test, ~rmse(model = .x, data = .y)))

# Checking for errors
bw_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

Based on the plots created with the code above, the model with all of the predictors had the highest RMSE, which means that it did not "fit" the data set as well as the other models. The model with only the main effect had the second lowest RMSE values, and the model with the interactions "fit" the data set the best. However, the RMSE values are still very high across the three models, so these models are not the most accurate in prediction. 
